Asymmetric relationships and their effects on coexistence: Supporting information

### 2023-07-31 paper/RefereeResponses1.tex

\noindent ***\emph{We have gone to great lengths to address the referee's specific suggestions below, and we have also redoubled our
efforts to make the manuscript as accessible as possible, generally. We appreciate being spurred to do so, thanks. } \\
%We have to redouble our efforts, as it says. Maybe we also want to point out somewhere that this particular
%sub-field is already a very technical one, but is nevertheless considered a mainstream and very important
%area in ecology? %food webs? networks

%I wrote the following, but decided not to include it here. Might include it elsewhere:
%The research field
%surrounding the MCT and mechanisms of coexistence is very important within ecology, but is nevertheless technical - see, for instance, the
%papers of Chesson, which have had enormous positive impact on the field, as well as the recent papers of Ellner which helped inspire
%our paper. All those papers, and many other papers in the field, are unavoidably technical, but have frequently been published
%in mainstream journals (the Ellner papers are in Ecology Letters) because of their importance and the importance of the subject
%matter they investigate. Though we agree with all efforts to make research results as clear as possible to non-technical audiences,
%we beg the referee

\noindent C37) At the beginning of the introduction the authors cite previous work to show the prevalence and importance of ATAs for population dynamics, and the stability of ecological communities, and Fig.1 illustrate what ATAs mean in a clear example, yet it is not well explained or at least it was not clear to me how ATA can either promote or hinder coexistence in these initial sentences. \\

\noindent ***\emph{The referee appears to want us to present an intuitive explanation for how ATA effects work, and that 
is certainly a good idea. We have invested substantial efforts into doing so, and think we have succeeded. Though the referee's comment above may 
be interpreted to suggest that they wanted us
to add such an explanation to first paragraph of the paper, the reader is not equiped to understand the explanation at that 
point, so we added a new paragraph later in the Introduction (it is now the
second-to-last paragraph in the Introduction) that begins establishing such an intuition. We also added some text to the end of
the second paragraph that adds to the intuitive understanding of how ATAs can influence coexistence through a concrete 
example. We also added a new paragraph to the 
Discussion (the second paragraph of the Discussion). These new Discussion 
paragraphs are also supported by two new SI sections and two new SI figures which 
explain, in detail, how the intuition established in the two new main text paragraphs emerges from the modelling (SI sections S11 
and S12, SI Figs S4 and S5).
%DAN: make sure these are the final numbers of these SI sections
We believe that intuition such as the new material establishes should always be based in formal theoretical and 
empirical work, so the focus of the paper remains on our expansion of the MCT and our results showing
the *importance* of ATA effects. Though we definitely think our additions giving an intuition for ATA effects are a large
improvement in the manuscript, so we thank the referee for spurring us to make these additions.  } \\
%DONE except the checking as noted above.

@@

\noindent C38) Then the explanation of the importance of ATAs is done in relationship with the explanation of the storage effect. In detail, the explanation of the storage effect is superb, ... \\

\noindent ***\emph{Thank you for the positive feedback! We have also added some text to the end of that paragraph giving a 
concrete case (water limitation) in which one may expect an influence of ATAs. We think the new text definitely
makes it more intuitive reasonable to explore ATA contributions to conexistence.} \\
%DONE

@@

\noindent C40) ATAs can not only modify the importance of the storage effect but also of other mechanisms such as relative non-linearity, which is based on how competition fluctuates in ways that favor the competitor. Could the authors briefly indicate how this could occur? \\

\noindent ***\emph{This cannot occur. ATAs can only influence storage effects, not the other mechanisms, as stated at
the top of section 2.4 and explained mathematically in the SI section cited there. Basically, as explained in 2.4, 
this is because ATAs are about covariation between $E$ and $C$, whereas the mechanisms other than storage effects
do not pertain at all to covariation. For instance, relative nonlinearity is about the effects of variation 
in $E$ or $C$, not covariation between them.} \\
%DONE

\noindent C41) The lottery model is used to illustrate the importance of ATAs, and two types of fecundities are taken 
into account (log-normal and beta), can the author explain why both are important, and later on the results and discussion 
why ATAs play a major role with beta fecundities and not with log-normal.
The model used for the chemostat is in its formulation quite different compared to the lottery model. Although the technical
details are left for the supplementary material, can the authors explain more in the detail in the main text how the 
importance of ATAs can be used for this particular model.\\

\noindent ***\emph{This is certainly a valid question, and we have gone to substantial lengths to address it. 
Partly in response to this comment and partly in response to earlier comments of referee 3, 
we added substantial new material providing intuitive explanations of ATA effects in the Introduction,
Discussion, and SI (see above responses). That new material also has information comparing the models
and explaining why ATA effects are substantial for the beta-fecundities lottery model and not as strong
for the log-normal fecundities lottery model. These are very positive additions to the manuscript, so we 
thank the referee for spurring us to add them. We also believe this is only a start -- additional explanations and intuitive 
explorations of ATA effects could and should be the subject of future papers. We've added as much material 
as possible on these topics to the current manuscript, given length limits and
requests from the referees to both simplify and add a variety of other content.} \\
%DONE

@@

\noindent C43) This study novelty is the focus on assymetric tail association between competition and environmental conditions as a mechanism of coexistence. \\

\noindent ***\emph{Thank you for pointing out the novelty.} \\

\noindent C44) The manuscript is very theoretical with a highly technical language hard to follow by a broad range of ecologists. My main suggestion is that the authors need to rewrite it in several parts to make it accessible and convincing. The authors have to make an effort to use a more biological/ecological language with reference to real world potential examples/cases/systems. Some mathematical material could be moved to Supplementary material. \\

%Need to address. However, this papers seems no more technical than the earlier Ellner paper. And, furthermore, 
%one of the referees (ref 1) actually asked us to put BACK technical content in the main text which we had 
%moved to the SI before submission to keep it less technical. Also, this research area is technical, though it
%is still central to ecology as a discipline. Recycle some of your arguments above about technical aspects. 
%That said, we do need to do a pass thu and figure out what technical content we can reduce, so we can make it
%as clear as it can be. Note also they say the math *could* be moved, suggesting less importance than 
%using ``a more biological/ecological language...''. So maybe let's try to do more of that, some of which
%I've alreday done thru answering the referee comments.
\noindent ***\emph{response} \\
